### 2004-07-07 Documentation/part1.tex
*** empty log message ***

@@

\bi
\item
 Obtaining rate vectors
\item
 Obtaining fluxes/cross sections etc.
\item
 ``Check''-functions
\ei

>>>>

\section{Version control}
\index{Version control}

In order to keep track of the used version of \GLOBES , the software
provides a number of functions to check the \GLOBES\ and experiment
versions. It is up to the user to implement mechanisms into the
program and \AEDL\ files to check wether
\begin{itemize}
\item
 The program should only run with this specific version of \GLOBES
\item
 The program can only run with a minimum version of \GLOBES
\item
 The program can only run up to a certain \GLOBES\ version.
\end{itemize}
The same holds for \AEDL\ files: For example, 
some features may not be supported by earlier versions of \GLOBES\ anymore.
The program can then check the version of the \AEDL\ file and break if it is
too old.

The functions in \GLOBES\ for version control are:
\begin{function}
\GLBNS{glbTestReleaseVersion}
{\tt int glbTestReleaseVersion(const char *version)} returns $0$ if
the {\tt version} string of the format ``X.Y.Z'' is exactly the
used \GLOBES\ version, $1$ if it is newer, and $-1$ if it is older. 
\end{function}
\begin{function}
\GLBNS{glbTestLibraryVersion}
{\tt int glbTestLibraryVersion(const char *version)} returns $0$ if
the {\tt version} string of the format ``X.Y.Z'' is exactly the
used \GLOBES\ version, $1$ if it is newer, and $-1$ if it is older.
Note that the library and \GLOBES\ versions are not the same. 
\end{function}
\begin{function}
\GLBNS{glbTestLibraryVersion}
{\tt int glbTestLibraryVersion(const char *version)} returns $0$ if
the {\tt version} string of the format ``X.Y.Z'' is exactly the
used \GLOBES\ version, $1$ if it is newer, and $-1$ if it is older.
Note that the library and \GLOBES\ versions are not the same. 
\end{function}
\begin{function}
\GLBNS{glbVersionOfExperiment} 
{\tt const char* glbVersionOfExperiment(int experiment)} returns
the version string of the experiment number {\tt experiment}.
The version string points to the experiment structure, which means
that it cannot be altered and does not have to be destroyed by the
user.
\end{function}

@@

In this chapter, we discuss possibilities to obtain low-level information
in \GLOBES , \ie, about oscillation probabilities, rates, and other
information lower than on the $\chi^2$-level.

\section{Oscillation probabilities}
\index{Oscillation probabilities}

\GLOBES\ can compute the probabilities in vacuum
with the following function:
\begin{function}
\GLBNS{glbVacuumProbability}
{\tt double glbVacuumProbability(int l, int m, int panti,double E, double L)} returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} and the baseline {\tt L} in vacuum. The parameter
{\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos. 
\end{function}
In addition, the oscillation probabilities in matter can be obtained
with:
\begin{function}
\GLBNS{glbProfileProbability}
{\tt double glbProfileProbability(int l, int m, int panti,double E)}
 returns the neutrino oscillation probability $\nu_l \rightarrow \nu_m$ for the energy {\tt E} in matter. The parameter
{\tt panti} is $+1$ for neutrinos and $-1$ for antineutrinos.
The matter density profile including baseline is the one from the last
evaluated experiment. 
\end{function}
THIS FUNCTION MAY OBTAIN AN EXPERIMENT INDEX (WW).
\section{Event rates}
\index{Event rates}
One can also return event rates in \GLOBES , but this feature
requires some knowledge about the experiment definition. \GLOBES\
currently supports rule-based and channel-based event rate functions,
where the information is in most cases written into a file.
The rule-based functions are:
\begin{function}
\GLBNS{glbShowRuleRates}
{\tt int glbShowRuleRates(FILE* stream, int exp, int rule, int pos,
int effi, int bgi, int coeffi, int signal)} prints the binned rule rates as
list with energy and event rate to the file {\tt stream} (either an
open file, or {\tt stdout}). A specific experiment {\tt exp} and a 
specific rule {\tt rule} have to be chosen, as well as the signal
or background rate {\tt signal} (either \GLB{GLB\_SIG} or \GLB{GLB\_BG}).
The position {\tt pos} refers to the component within the signal or 
background, and can also be {\tt GLB\_ALL}. The function may return
the rates with (\GLB{GLB\_W\_COEFF}) or without (\GLB{GLB\_WO\_COEFF})
overall efficieny coefficient, as it is specified by {\tt coeffi}. 
In addition, it may contain the post-smearing efficiencies (set
{\tt effi} to \GLB{GLB\_W\_EFF} or \GLB{GLB\_WO\_EFF}), and the
post-smearing backgrounds (set
{\tt bgi} to \GLB{GLB\_W\_BG} or \GLB{GLB\_WO\_BG}). The pre-smearing
efficiencies and backgrounds cannot be accessed at the rule level.
The return value
is $0$ if successful, and $-1$ if unsuccessful.
\end{function}
\begin{function}
\GLBNS{glbShowTotalRuleRates}
{\tt double glbShowTotalRuleRates(int exp, int rule, int pos,
int effi, int bgi, int coeffi, int signal)} returns the total rates with
the same parameters as {\tt glbShowRuleRates}.
\end{function}
(THIS SYNTAX NEEDS TO BE CHECKED, BECAUSE FUNCTION IS NOT YET IMPLEMENTED - WW)

The function {\tt glbShowTotalRuleRates} is especially useful if
one wants to draw bi-rate graphs with total event rates, or look
for the $(\deltacp,\theta_{13})$-degeneracy by the intersection of 
neutrino and antineutrino constant event rate curves.

In addition, \GLOBES\ has a channel-based rate function:
\begin{function}
\GLBNS{glbShowChannelRates}
{\tt int glbShowChannelRates(FILE *stream,
int exp, int channel, int smearing, int effi, int bgi)}
prints the binned channel rates as
list with energy and event rate to the file {\tt stream} (either an
open file, or {\tt stdout}). A specific experiment {\tt exp} and a 
specific channel {\tt channel} have to be chosen.
The function may return
the rates before (\GLB{GLB\_PRE}) or after (\GLB{GLB\_POST})
the energy smearing, as it is specified by {\tt smearing}.
In addition, it may contain the pre- and post-smearing efficiencies (set
{\tt effi} to \GLB{GLB\_W\_EFF} or \GLB{GLB\_WO\_EFF}), and the
pre- and post-smearing backgrounds (set
{\tt bgi} to \GLB{GLB\_W\_BG} or \GLB{GLB\_WO\_BG}). Note that
the post-smearing efficiencies and backgrounds cannot be taken into
account if the rates are returned before the energy smearing.
The return value
is $0$ if successful, and $-1$ if unsuccessful.
\end{function}

\section{Fluxes and cross sections}
\index{Flux} \index{Cross section}

Another piece of low-level information, which can be returned by \GLOBES ,
are the numbers from the loaded fluxes and cross sections.
The following functions interpolate on the loaded fluxes and cross 
sections, \ie, any value in the allowed energy range can be given as input:
\begin{function}
\GLBNS{glbFlux}
{\tt double glbFlux(int exp, int ident, 
double E, double distance, int l, int anti)} returns
the flux of flux number {\tt ident} of the experiment {\tt exp}
for the flavor $\nu_l$ 
and polarity {\tt anti} ($+1$: neutrinos, $-1$: antineutinos) at the energy {\tt E} and distance {\tt distance}.
\end{function}

\begin{function}
\GLBNS{glbXSection}
{\tt double glbXSection(int ident, double E, int l, int anti)} returns
the cross section of cross section number {\tt ident} for the flavor $\nu_l$ 
and polarity {\tt anti} ($+1$: neutrinos, $-1$: antineutinos) at the energy {\tt E}.
\end{function}
Note that all flux or flavor numbers run from $0$ to $N-1$ in these functions.

(THIS FUNCTION MAY GET AN EXPERIMENT INDEX IF NOT THROUGH-COUNTED IN AEDL!)
